Component response rate variation drives stability in large complex systems

### 2018-06-08 notebook/SI.Rmd
Fix Issue #2 in the SI; dummy index removed from all ecological tables

```{r, echo = FALSE}
cd_tab <- cdat[,1:7];
kable(cd_tab);
```

@@

```{r, echo = FALSE}
md_tab <- mdat[,1:7];
kable(md_tab);
```

@@

```{r, echo = FALSE}
pd_tab <- pdat[,1:7];
kable(pd_tab);
```

>>>>

```{r, echo = FALSE}
cd_tab <- cdat[,2:7];
kable(cd_tab);
```

@@

```{r, echo = FALSE}
md_tab <- mdat[,2:7];
kable(md_tab);
```

@@

```{r, echo = FALSE}
pd_tab <- pdat[,2:7];
kable(pd_tab);
```
